---
title: "GEE Vector Ecozone Attribute Creation"
author: "Anna Talucci"
date: "3/11/2021"
output: html_document
---


# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

Here we  add attributes, clip to ecozone extent, add ecozone attributes, designate as arctic or sub arctic, and add attributes from hotspot data (e.g., fire start).



# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(tidyr)
library(spatialEco)
library(ggplot2)
library(lubridate)
```

# Projections

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## Fire perimeters
```{r}
fires = st_read("../data/2.2-GEE-clean-shapefiles-EqualArea/nbuf_equalarea_2014.shp", "nbuf_equalarea_2014") 
```



## Hotspots
```{r}
hotspots = st_read("../data/M6-march-october/M6_mar-oct_2014.shp", "M6_mar-oct_2014") 
```

## Ecozones Polygon
```{r}
ecozones = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee") 
```

## Arctic Polygon
Cropped ecozones to arctic circle for arctic designation. 

```{r}
eco_arctic = st_read("../data/bbox/ecozone_arctic_crop_ee.shp", "ecozone_arctic_crop_ee") 
```

# Convert to Equal Area

```{r}
fires_ea = st_transform(fires, ea_ru)
hotspots_ea = st_transform(hotspots, ea_ru)
ecozones_ea = st_transform(ecozones, ea_ru)
eco_arctic_ea = st_transform(eco_arctic, ea_ru)
```


# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr
- Removed fires less than 400 ha
- Ecozone
- Arctic/subarctic

## Area Burned Attributes
```{r}
fires_at = fires_ea %>%
  dplyr::mutate(ID_obj = row_number()) %>% 
  dplyr::mutate(burned_area_m = as.numeric(round(st_area(fires_ea),1))) %>% 
  dplyr::mutate(burned_area_ha = as.numeric(round(burned_area_m*0.0001, 1))) %>% 
  dplyr::mutate(fire_yr = 2014) 
```


```{r}
fires_at
```

# Plot
```{r eval=FALSE, include=FALSE}
plot(st_geometry(ecozones_ea), col = sf.colors(12, categorical = TRUE), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at)), pch = 3, col = 'red', add = TRUE)
```

## Ecozone attributes

We use `st_join` to add the attributes of the ecozone for each fire. Fires are not restricted to within individual ecozone boundaries. In order to avoid a duplicate entry for a fire that spans two ecozones, we add the argument `largest=TRUE`, which assigns the ecozone that contrains the majority of the fire. 

```{r}
head(ecozones_ea)
```

### Rename columns for  ecozones
Note about  attributes
1. AREA - area for individual polygons
2. area_km^2 - total area for each ecoregion ( 1 km^ is 100 ha)
```{r}
ren_ecozones_ea = ecozones_ea %>% 
  rename(c("eco_objectID" = "OBJECTID", "eco_area" = "AREA" , "eco_realm" = "REALM", "eco_biome" = "BIOME")) %>%
  dplyr::mutate(eco_area_ha = as.numeric(round(area_km2*100, 1)))
```

```{r}
head(ren_ecozones_ea)
```

### Join ecozone attributes with fire perimeters
st_make_valid(poly)
```{r}
fires_at_eco = st_join(st_make_valid(fires_at), ren_ecozones_ea, largest=TRUE) %>% dplyr::select(rmpshpr:eco_area, ECO_NAME:ECO_SYM, area_km2:geometry) %>% 
  drop_na(eco_code)
```
%>% dplyr::select(rmpshpr:eco_area, ECO_NAME:ECO_SYM, area_km2:geometry) %>% 
  drop_na(eco_code)
```{r}
head(fires_at_eco)
```

##  Plot
```{r eval=FALSE, include=FALSE}
plot(st_geometry(ecozones_ea), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco)), pch = 3, col = 'red', add = TRUE)
```

## Arctic/Subarctic designation
```{r}
fires_at_eco_arc = st_join(fires_at_eco, eco_arctic_ea, largest=TRUE) 
```

```{r}
str(fires_at_eco_arc)
```

### Convert NA to subarctic
For location, arctic and subarctic, we need to redefine the NA values as subartic
```{r}
fires_at_eco_arc$location <- factor(fires_at_eco_arc$location, exclude = NULL, 
               levels = c("arctic", NA), 
               labels = c("arctic", "subarctic"))
fires_at_eco_arc
```

```{r eval=FALSE, include=FALSE}
plot(st_geometry(ecozones_ea), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc)), pch = 3, col = 'red', add = TRUE)
```

### Save as test version to check
```{r eval=FALSE, include=FALSE}
st_write(fires_at_eco_arc, "../outputs/test/test_fires_at_eco_arc.shp", driver="ESRI Shapefile") 

```

## Hotspot attributes
```{r}
str(hotspots_ea)
```

```{r}
hotspots_ea %>% mutate(julian_date = yday(ACQ_DATE)) %>% 
  separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) 
```


### Function to summarize hotspot attributes
```{r}
sum_pt_poly = function(x){
  x %>% mutate(julian_date = yday(ACQ_DATE)) %>%
  separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) %>% group_by(ID_obj) %>% 
  summarize(min_julian_date = min(julian_date),
            max_julian_date = max(julian_date),
            mean_julian_date = mean(julian_date),
            median_julian_date = median(julian_date),
            min_confidence = min(CONFIDENCE), 
            max_confidence = max(CONFIDENCE), 
            mean_confidence = mean(CONFIDENCE), 
            median_confidence = median(CONFIDENCE),
            min_acq_date = min(ACQ_DATE), 
            max_acq_date = max(ACQ_DATE)) -> x
  return(x)
}
```


```{r}
fires_at_eco_arc_hs = st_intersection(hotspots_ea, fires_at_eco_arc) %>% sum_pt_poly()

```

```{r}
head(fires_at_eco_arc_hs)
```
```{r eval=FALSE, include=FALSE}
plot(st_geometry(ecozones_ea), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc_hs)), pch = 3, col = 'red', add = TRUE)
```
### Drop geometry from hotspot attributes

```{r}
st_geometry(fires_at_eco_arc_hs) <- NULL
```

## Merge  attributes
Merge attributes into single shapefile
```{r}
fires_at_eco_arc_hs_merge = merge(fires_at_eco_arc, fires_at_eco_arc_hs, by="ID_obj")
```

```{r}
head(fires_at_eco_arc_hs_merge)
```


```{r eval=FALSE, include=FALSE}
plot(st_geometry(ecozones_ea), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc_hs_merge)), pch = 3, col = 'red', add = TRUE)
```


## Add unique fire ID

```{r}
head(fires_at_eco_arc_hs_merge)
```
Fire ID components
1. RU
2. YEAR
3. Ecozone code
4. Start date

An add fire length in days

```{r}
fires_at_eco_arc_hs_merge_burn = fires_at_eco_arc_hs_merge %>%
  separate(min_acq_date, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) %>%
  mutate(burn_days = (max_julian_date - min_julian_date)) %>%
  mutate(Fire_ID = paste("RU_", fire_yr,"_", eco_code, "_", acq_year, acq_month, acq_day, sep = "")) 

```

```{r}
fires_at_eco_arc_hs_merge_burn_rh = nngeo::st_remove_holes(fires_at_eco_arc_hs_merge_burn, max_area = 1000)
```




# Write to shapefile
```{r}
st_write(fires_at_eco_arc_hs_merge_burn_rh, "../outputs/2.3-GEE-Attribute-Shapefiles-EqualArea/SiberiaFires_2014.shp", driver="ESRI Shapefile") 
```


