---
title: "Bounding Boxes"
author: "Anna Talucci"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview

What is included in this script:

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
```

# Projections
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```


Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Create Bounding Box for FLARE

Define coordinates in a matrix as Longitude, lattitude from Upper Left to Upper right, to lower right, to lower left 

## FLARE coordinates 

```{r}
coords_flare = matrix(c(118.94, 72.26,
               171.0, 72.26,
               171.0, 60.0, 
               118.94, 60.0), 
             ncol = 2, byrow = TRUE)
```

## NE Siberia coordinates 

```{r}
coords_neSiberia = matrix(c(118.0, 74.26,
               190.25, 74.26,
               190.25, 60.0, 
               118.0, 60.0), 
             ncol = 2, byrow = TRUE)
```



## Far NE Siberia coordinates 

```{r}
coords_FneSiberia = matrix(c(170.5, 74.26,
               190.25, 74.26,
               190.25, 60.0, 
               170.5, 60.0), 
             ncol = 2, byrow = TRUE)
```

## Yakutsk Bounding Box
Long, Lat
UL 129.9975, 63.7097
UR 137.2975, 63.7097
LR 137.2975, 61.3456
LL 129.9975, 61.3456
```{r}
coords_yak = matrix(c(129.99, 63.70,
               137.29, 63.70,
               137.29, 61.34, 
               129.99, 61.34), 
             ncol = 2, byrow = TRUE)
```

## Convert to Polygon
```{r}
flare_coord = Polygon(coords_flare)
nesiberia_coord = Polygon(coords_neSiberia)

Fne_coord = Polygon(coords_FneSiberia)
yak_coord = Polygon(coords_yak)
```




```{r}
flare_poly = SpatialPolygons(list(Polygons(list(flare_coord), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

ne_poly = SpatialPolygons(list(Polygons(list(nesiberia_coord), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

Fne_poly = SpatialPolygons(list(Polygons(list(Fne_coord), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

yak_poly = SpatialPolygons(list(Polygons(list(yak_coord), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```



## Plot
```{r}
plot(flare_poly, axes = TRUE)
```

```{r}
plot(Fne_poly, axes = TRUE)
```

```{r}
plot(yak_poly, axes = TRUE)
```

## Convertfrom sp to sf

```{r}
flare_sf = st_as_sf(flare_poly) 
ne_sf = st_as_sf(ne_poly)
Fne_sf = st_as_sf(Fne_poly)
yak_sf = st_as_sf(yak_poly) 
```

```{r}
AC_sf = st_as_sf(AC_poly)
```


## Write bounding box to shapefile

```{r eval=FALSE, include=FALSE}
st_write(flare_sf, "../outputs/bbox/FLARE_bbox.shp", driver="ESRI Shapefile")  # create to a shapefile 

st_write(ne_sf, "../outputs/bbox/neSiberia_bbox.shp", driver="ESRI Shapefile")

st_write(Fne_sf, "../outputs/bbox/FarNE_bbox.shp", driver="ESRI Shapefile")

st_write(yak_sf, "../outputs/bbox/yakutsk_bbox.shp", driver="ESRI Shapefile")
```

```{r}

st_write(AC_sf, "../outputs/bbox/ArcticCircle_bbox.shp", driver="ESRI Shapefile")
```

# Arctic Circle Bounding Box
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```

```{r}
head(arctic)
```

```{r}
arctic$geometry
```


## define coordinates 
Long, Lat
UL 129.9975, 63.7097
UR 137.2975, 63.7097
LR 137.2975, 61.3456
LL 129.9975, 61.3456
```{r}
coords_ArcticCircle = matrix(c(75.0, 80.0,
               190.25, 80.0,
               190.25, 66.5, 
               75.0, 66.5), 
             ncol = 2, byrow = TRUE)
```

## convert to polygon

```{r}
AC_coord = Polygon(coords_ArcticCircle)
```

## add projection
```{r}
AC_poly = SpatialPolygons(list(Polygons(list(AC_coord), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

```

## Convert to sf
```{r}
AC_sf = st_as_sf(AC_poly) 

```

## Equal Area to overlay on Ecozones
```{r}
AC_ee = spTransform(AC_poly, CRS(ee_russia))
```


```{r}
arctic_ee = st_transform(arctic, ee_russia)
```


## Plot data
```{r}
plot(eco_ee)
plot(AC_ee, add=TRUE)
plot(arctic_ee, add=TRUE)
```

```{r}

a = st_crop(eco_ee, arctic_ee)
plot(a)
```

```{r eval=FALSE, include=FALSE}
st_write(AC_sf, "../outputs/bbox/arctic_circle_ecozone.shp", driver="ESRI Shapefile") 

```

# Crop Ecozone for arctic boundary 
```{r}
ecozone1 = st_read("../data/ecozones/ne_siberia_ecozones_ee.shp", "ne_siberia_ecozones_ee") 
```

```{r}
eco_wgs = st_transform(ecozone1, wgs_proj)
```
 st_transform(crs("+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=sphere +units=m +no_defs"))
```{r}
eco_wgs_crop = eco_wgs %>% st_crop(y = st_bbox(c(xmin = -180, ymin = 66.45, xmax = 180, ymax = 90))) 
```

```{r}
eco_crop_ee = st_transform(eco_wgs_crop, ee_russia)
```

```{r}
plot(eco_crop_ee$geometry)
plot(arctic_ee, add=TRUE)
```

```{r}
head(eco_crop_ee)
```

```{r}
arctic_eco_bounds = eco_crop_ee %>% dplyr::mutate(location = "arctic") %>% dplyr::select(location)
```


```{r eval=FALSE, include=FALSE}
st_write(arctic_eco_bounds, "../outputs/bbox/ecozone_arctic_crop_ee.shp", driver="ESRI Shapefile") 

```

# Create Bounding Boxes for Ecozone Extent

## Equal Area Ecozones
```{r}
eco_ee = readOGR("../data/ecozones/ne_siberia_ecozones_ee.shp", "ne_siberia_ecozones_ee") 
```

**Ecozone Extent from ecozone layer**
bbox:           xmin: -180 ymin: 50.13147 xmax: 180 ymax: 77.76253
bbox:           xmin: 130.1842 ymin: 68.56218 xmax: 161.9283 ymax: 72.9427
bbox:           xmin: 79.01171 ymin: 64.7211 xmax: 130.4216 ymax: 77.79169
bbox:           xmin: 86.27558 ymin: 50.10451 xmax: 142.6297 ymax: 71.44453
bbox:           xmin: 124.9269 ymin: 58.78296 xmax: 170.2515 ymax: 71.75275
bbox:           xmin: -179.9998 ymin: 59.77511 xmax: 179.9998 ymax: 70.15549
bbox:           xmin: -179.9995 ymin: 64.20744 xmax: 179.9971 ymax: 69.00497

**Create 3 ecozones to span the ecozones we are interested and deal with the Chukchi Peninsula**
1. Ecozones west xmin: 78 ymin: 50.0 xmax: 129 ymax: 78.0
2. Ecozones east xmin:  128.5 ymin: 50.0 xmax: 180 ymax: 78.0
3. Ecozones Chukchi xmin: -180 ymin: 50.0 xmax: -168 ymax: 78.0

How to formate the matrix for the bounding box
matrix(c(xmin, ymax,
               xmax, ymax,
               xmax, ymin, 
               xmin, ymin), 
             ncol = 2, byrow = TRUE)
```{r}
eco_west = matrix(c(78.0, 78.0,
               129.0, 78.0,
               129.0, 50.0, 
               78.0, 50.0), 
             ncol = 2, byrow = TRUE)


eco_west_coords = Polygon(eco_west)
eco_west_bbox = SpatialPolygons(list(Polygons(list(eco_west_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(eco_west_bbox)
```
```{r}
eco_nwest = matrix(c(78.0, 78.0,
               129.0, 78.0,
               129.0, 63.75, 
               78.0, 63.75), 
             ncol = 2, byrow = TRUE)


eco_nwest_coords = Polygon(eco_nwest)
eco_nwest_bbox = SpatialPolygons(list(Polygons(list(eco_nwest_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```
```{r}
eco_swest = matrix(c(78.0, 64.0,
               129.0, 64.0,
               129.0, 50.0, 
               78.0, 50.0), 
             ncol = 2, byrow = TRUE)


eco_swest_coords = Polygon(eco_swest)
eco_swest_bbox = SpatialPolygons(list(Polygons(list(eco_swest_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
eco_east = matrix(c(128.5, 78.0,
               180.0, 78.0,
               180.0, 50.0, 
               128.5, 50.0), 
             ncol = 2, byrow = TRUE)


eco_east_coords = Polygon(eco_east)
eco_east_bbox = SpatialPolygons(list(Polygons(list(eco_east_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
eco_neast = matrix(c(128.5, 78.0,
               180.0, 78.0,
               180.0, 63.5, 
               128.5, 63.5), 
             ncol = 2, byrow = TRUE)


eco_neast_coords = Polygon(eco_neast)
eco_neast_bbox = SpatialPolygons(list(Polygons(list(eco_neast_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```
```{r}
eco_seast = matrix(c(128.5, 64.0,
               180.0, 64.0,
               180.0, 50.0, 
               128.5, 50.0), 
             ncol = 2, byrow = TRUE)


eco_seast_coords = Polygon(eco_seast)
eco_seast_bbox = SpatialPolygons(list(Polygons(list(eco_seast_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(eco_east_bbox)
```

```{r}
eco_chukchi = matrix(c(-168.0, 78.0,
               -180.0, 78.0,
               -180.0, 50.0, 
               -168.0, 50.0), 
             ncol = 2, byrow = TRUE)


eco_chukchi_coords = Polygon(eco_chukchi)
eco_chukchi_bbox = SpatialPolygons(list(Polygons(list(eco_chukchi_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(eco_chukchi_bbox)
```
### Convert to sf
```{r}
eco_west_sf = st_as_sf(eco_west_bbox) 
eco_east_sf = st_as_sf(eco_east_bbox)

eco_nwest_sf = st_as_sf(eco_nwest_bbox) 
eco_neast_sf = st_as_sf(eco_neast_bbox)

eco_swest_sf = st_as_sf(eco_swest_bbox) 
eco_seast_sf = st_as_sf(eco_seast_bbox)

eco_chukchi_sf = st_as_sf(eco_chukchi_bbox)

```

### Equal Area to overlay on Ecozones
```{r}
eco_west_bbox_ee = spTransform(eco_west_bbox, CRS(ee_russia))
eco_east_bbox_ee = spTransform(eco_east_bbox, CRS(ee_russia))
eco_chukchi_bbox_ee = spTransform(eco_chukchi_bbox, CRS(ee_russia))
```



### Plot data
```{r}
plot(eco_ee)
plot(eco_west_bbox_ee, add=TRUE)
plot(eco_east_bbox_ee, add=TRUE)
plot(eco_chukchi_bbox_ee, add=TRUE)
```


```{r eval=FALSE, include=FALSE}
st_write(eco_west_sf, "../outputs/bbox/eco_west.shp", driver="ESRI Shapefile")  # create to a shapefile 

st_write(eco_east_sf, "../outputs/bbox/eco_east.shp", driver="ESRI Shapefile")

st_write(eco_chukchi_sf, "../outputs/bbox/eco_chukchi.shp", driver="ESRI Shapefile")

st_write(eco_nwest_sf, "../outputs/bbox/eco_nwest.shp", driver="ESRI Shapefile")
st_write(eco_swest_sf, "../outputs/bbox/eco_swest.shp", driver="ESRI Shapefile")# create to a shapefile 

st_write(eco_neast_sf, "../outputs/bbox/eco_neast.shp", driver="ESRI Shapefile")
st_write(eco_seast_sf, "../outputs/bbox/eco_seast.shp", driver="ESRI Shapefile")

```

#BBOX based on smaller ecozone area
```{r}
ckmt_nst_nsct = matrix(c(135.0, 72.5,
               171.0, 72.5,
               171.0, 55.0, 
               135.0, 55.0), 
             ncol = 2, byrow = TRUE)


ckmt_nst_nsct_coords = Polygon(ckmt_nst_nsct)
ckmt_nst_nsct_bbox = SpatialPolygons(list(Polygons(list(ckmt_nst_nsct_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
tcst_n = matrix(c(135.0, 77.0,
               79.0, 77.0,
               79.0, 70.0, 
               135.0, 70.0), 
             ncol = 2, byrow = TRUE)


tcst_n_coords = Polygon(tcst_n)
tcst_n_bbox = SpatialPolygons(list(Polygons(list(tcst_n_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
tcst_s = matrix(c(135.0, 70.0,
               79.0, 70.0,
               79.0, 63.0, 
               135.0, 63.0), 
             ncol = 2, byrow = TRUE)


tcst_s_coords = Polygon(tcst_s)
tcst_s_bbox = SpatialPolygons(list(Polygons(list(tcst_s_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```


```{r}
est_tbbmt_n = matrix(c(135.0, 63.0,
               79.0, 63.0,
               79.0, 56.0, 
               135.0, 56.0), 
             ncol = 2, byrow = TRUE)


est_tbbmt_n_coords = Polygon(est_tbbmt_n)
est_tbbmt_n_bbox = SpatialPolygons(list(Polygons(list(est_tbbmt_n_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
est_tbbmt_s = matrix(c(135.0, 56.0,
               79.0,56.0,
               79.0, 48.0, 
               135.0, 48.0), 
             ncol = 2, byrow = TRUE)


est_tbbmt_s_coords = Polygon(est_tbbmt_s)
est_tbbmt_s_bbox = SpatialPolygons(list(Polygons(list(est_tbbmt_s_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cpt_bt_east = matrix(c(179.99, 71.0,
               170.0, 71.0,
               170.0, 59.0, 
               179.99, 59.0), 
             ncol = 2, byrow = TRUE)


cpt_bt_east_coords = Polygon(cpt_bt_east)
cpt_bt_east_bbox = SpatialPolygons(list(Polygons(list(cpt_bt_east_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cpt_bt_west = matrix(c(-179.99, 71.0,
               -168.0, 71.0,
               -168.0, 59.0, 
               -179.99, 59.0), 
             ncol = 2, byrow = TRUE)


cpt_bt_west_coords = Polygon(cpt_bt_west)
cpt_bt_west_bbox = SpatialPolygons(list(Polygons(list(cpt_bt_west_coords), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

### Convert to sf
```{r}
ckmt_nst_nsct_sf = st_as_sf(ckmt_nst_nsct_bbox) 
tcst_n_sf = st_as_sf(tcst_n_bbox) 
tcst_s_sf = st_as_sf(tcst_s_bbox)
est_tbbmt_n_sf = st_as_sf(est_tbbmt_n_bbox)
est_tbbmt_s_sf = st_as_sf(est_tbbmt_s_bbox)
cpt_bt_west_sf = st_as_sf(cpt_bt_west_bbox)
cpt_bt_east_sf = st_as_sf(cpt_bt_east_bbox)
```

### Equal Area to overlay on Ecozones
```{r}
ckmt_nst_nsct_bbox_ee = spTransform(ckmt_nst_nsct_bbox, CRS(ee_russia))
tcst_n_bbox_ee = spTransform(tcst_n_bbox, CRS(ee_russia))
tcst_s_bbox_ee = spTransform(tcst_s_bbox, CRS(ee_russia))
est_tbbmt_n_bbox_ee = spTransform(est_tbbmt_n_bbox, CRS(ee_russia))
est_tbbmt_s_bbox_ee = spTransform(est_tbbmt_s_bbox, CRS(ee_russia))
cpt_bt_west_bbox_ee = spTransform(cpt_bt_west_bbox, CRS(ee_russia))
cpt_bt_east_bbox_ee = spTransform(cpt_bt_east_bbox, CRS(ee_russia))
```



### Plot data
```{r}
plot(eco_ee)
plot(ckmt_nst_nsct_bbox_ee, add=TRUE)
plot(tcst_n_bbox_ee, add=TRUE)
plot(tcst_s_bbox_ee, add=TRUE)
plot(est_tbbmt_n_bbox_ee, add=TRUE)
plot(est_tbbmt_s_bbox_ee, add=TRUE)
plot(cpt_bt_west_bbox_ee, add=TRUE)
plot(cpt_bt_east_bbox_ee, add=TRUE)
```


```{r eval=FALSE, include=FALSE}
st_write(ckmt_nst_nsct_sf, "../outputs/bbox/ckmt_nst_nsct.shp", driver="ESRI Shapefile") 
st_write(tcst_n_sf, "../outputs/bbox/tcst_n.shp", driver="ESRI Shapefile") 

st_write(tcst_s_sf, "../outputs/bbox/tcst_s.shp", driver="ESRI Shapefile") 

st_write(est_tbbmt_n_sf, "../outputs/bbox/est_tbbmt_n.shp", driver="ESRI Shapefile") 
st_write(est_tbbmt_s_sf, "../outputs/bbox/est_tbbmt_s.shp", driver="ESRI Shapefile") 

st_write(cpt_bt_west_sf, "../outputs/bbox/cpt_bt_west.shp", driver="ESRI Shapefile") 
st_write(cpt_bt_east_sf, "../outputs/bbox/cpt_bt_east.shp", driver="ESRI Shapefile") 



```
