---
title: "2020 hotspots"
author: "Anna Talucci"
date: "11/17/2020"
output: html_document
---

# Overview

Combine Modis and VIIRS point data into single files.
Data acquired from [FIRMS](https://firms.modaps.eosdis.nasa.gov/download/create.php)

Description of [Modis and VIIRS data]( https://earthdata.nasa.gov/earth-observation-data/near-real-time/firms)

VIIRS launch October 2011, fire season data available 2012-present
MODIS launch    , available 2001-present

Only running on 2012-2020 since those years are the only ones with overlap.

Annual point data from January to December.

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
```


# Data


## Modis and VIIRS for 2012-2020
```{r}
m_2020 = st_read("../data/FIRMS-PointData-raw/firms_2020/fire_archive_M6_2020.shp", "fire_archive_M6_2020")
v_2020 = st_read("../data/FIRMS-PointData-raw/firms_2020/fire_archive_V1_2020.shp", "fire_archive_V1_2020")

m_2019 = st_read("../data/FIRMS-PointData-raw/firms_2019/fire_archive_M6_2019.shp", "fire_archive_M6_2019")
v_2019 = st_read("../data/FIRMS-PointData-raw/firms_2019/fire_archive_V1_2019.shp", "fire_archive_V1_2019")

m_2018 = st_read("../data/FIRMS-PointData-raw/firms_2018/fire_archive_M6_2018.shp", "fire_archive_M6_2018")
v_2018 = st_read("../data/FIRMS-PointData-raw/firms_2018/fire_archive_V1_2018.shp", "fire_archive_V1_2018")

m_2017 = st_read("../data/FIRMS-PointData-raw/firms_2017/fire_archive_M6_2017.shp", "fire_archive_M6_2017")
v_2017 = st_read("../data/FIRMS-PointData-raw/firms_2017/fire_archive_V1_2017.shp", "fire_archive_V1_2017")

m_2016 = st_read("../data/FIRMS-PointData-raw/firms_2016/fire_archive_M6_2016.shp", "fire_archive_M6_2016")
v_2016 = st_read("../data/FIRMS-PointData-raw/firms_2016/fire_archive_V1_2016.shp", "fire_archive_V1_2016")

m_2015 = st_read("../data/FIRMS-PointData-raw/firms_2015/fire_archive_M6_2015.shp", "fire_archive_M6_2015")
v_2015 = st_read("../data/FIRMS-PointData-raw/firms_2015/fire_archive_V1_2015.shp", "fire_archive_V1_2015")

m_2014 = st_read("../data/FIRMS-PointData-raw/firms_2014/fire_archive_M6_2014.shp", "fire_archive_M6_2014")
v_2014 = st_read("../data/FIRMS-PointData-raw/firms_2014/fire_archive_V1_2014.shp", "fire_archive_V1_2014")

m_2013 = st_read("../data/FIRMS-PointData-raw/firms_2013/fire_archive_M6_2013.shp", "fire_archive_M6_2013")
v_2013 = st_read("../data/FIRMS-PointData-raw/firms_2013/fire_archive_V1_2013.shp", "fire_archive_V1_2013")

m_2012 = st_read("../data/FIRMS-PointData-raw/firms_2012/fire_archive_M6_2012.shp", "fire_archive_M6_2012")
v_2012 = st_read("../data/FIRMS-PointData-raw/firms_2012/fire_archive_V1_2012.shp", "fire_archive_V1_2012")
```

```{r}
head(m_2012)

```

```{r}

head(v_2012)
```
```{r}
summary(m_2012)
```
```{r}
summary(v_2012)
```

```{r}
names(m_2012)
```

```{r}
names(v_2012)
```

## Drop columns that do not match
### Modis
```{r}
m_2012 = m_2012 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2013 = m_2013 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2014 = m_2014 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2015 = m_2015 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2016 = m_2016 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2017 = m_2017 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2018 = m_2018 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2019 = m_2019 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
m_2020 = m_2020 %>% dplyr::select(-BRIGHTNESS, -BRIGHT_T31)
```

###VIIRS
```{r}
v_2012 = v_2012 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2013 = v_2013 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2014 = v_2014 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2015 = v_2015 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2016 = v_2016 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2017 = v_2017 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2018 = v_2018 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2019 = v_2019 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)
v_2020 = v_2020 %>% dplyr::select(-BRIGHT_TI4, -BRIGHT_TI5)

```

## COmbine MODIS and VIIRS into one Shapefile
```{r}
vm_2012 = rbind(m_2012, v_2012)
vm_2013 = rbind(m_2013, v_2013)
vm_2014 = rbind(m_2014, v_2014)
vm_2015 = rbind(m_2015, v_2015)
vm_2016 = rbind(m_2016, v_2016)
vm_2017 = rbind(m_2017, v_2017)
vm_2018 = rbind(m_2018, v_2018)
vm_2019 = rbind(m_2019, v_2019)
vm_2020 = rbind(m_2020, v_2020)
```


# Check Data
```{r}
summary(vm_2020)
```


```{r eval=FALSE, warning=FALSE, include=FALSE}
st_write(vm_2012, "../outputs/hotspot-point-combine/hotspot_point_2012.shp", driver="ESRI Shapefile")
st_write(vm_2013, "../outputs/hotspot-point-combine/hotspot_point_2013.shp", driver="ESRI Shapefile")
st_write(vm_2014, "../outputs/hotspot-point-combine/hotspot_point_2014.shp", driver="ESRI Shapefile")
st_write(vm_2015, "../outputs/hotspot-point-combine/hotspot_point_2015.shp", driver="ESRI Shapefile")
st_write(vm_2016, "../outputs/hotspot-point-combine/hotspot_point_2016.shp", driver="ESRI Shapefile")
st_write(vm_2017, "../outputs/hotspot-point-combine/hotspot_point_2017.shp", driver="ESRI Shapefile")
st_write(vm_2018, "../outputs/hotspot-point-combine/hotspot_point_2018.shp", driver="ESRI Shapefile")
st_write(vm_2019, "../outputs/hotspot-point-combine/hotspot_point_2019.shp", driver="ESRI Shapefile")
st_write(vm_2020, "../outputs/hotspot-point-combine/hotspot_point_2020.shp", driver="ESRI Shapefile")

```