---
title: "Ecozone Climate Data"
author: "Anna Talucci"
date: "11/15/2020"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Overview

GEE data 

Climate data from Terra Climate 

Temperature (degrees celcius) scale = 0.1
precipitation (mm) no scaling

Monthly data


***
# Data Details
[Terra Climate](https://developers.google.com/earth-engine/datasets/catalog/IDAHO_EPSCOR_TERRACLIMATE)

Name  |	Units	| Scale	| Description
------|-------|-------|------------
aet	  | mm	  |	0.1	  | Actual evapotranspiration,  
def	  | mm	  |	0.1	  | Climate water deficit, 
pdsi	|       |	0.01	| Palmer Drought Severity Index
pet	  | mm	  |	0.1	  | Reference evapotranspiration (ASCE Penman-Montieth)
pr	  | mm		|	      | Precipitation accumulation
ro	  | mm	  |       |	Runoff, derived using a one-dimensional soil water balance model
soil	| mm	  | 0.1	  | Soil moisture, derived using a one-dimensional soil water balance model
srad	| W/m^2	|	0.1	  | Downward surface shortwave radiation
swe	  | mm	  |		    | Snow water equivalent, 
tmmn	| 째C	  |	0.1	  | Minimum temperature
tmmx	| 째C	  |	0.1	  | Maximum temperature
vap	  | kPa	  |	0.001	| Vapor pressure
vpd   |	kPa	  |	0.01	| Vapor pressure deficit
vs	  | m/s	  |	0.01	| Wind-speed at 10m

***

# Packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
```

# Define graph Theme and color Palette 

```{r}
boxplot_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
theme(panel.grid = element_blank(),
        panel.border = element_blank())
```{r}
reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 10, hjust = 0.5, vjust = -0.2),
        axis.title.y = element_text(size = 10, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 9, color = "black"),
        axis.text.y = element_text(size = 9, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```



# Data
```{r}
list_of_files <- list.files(path = "../data/climate-ecozone",
                            full.names = TRUE)
list_of_files
df <- list_of_files %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name")

summary(df)
```

```{r}
df1 = df %>% 
  separate(file_name, c("A","B","C","D","E","F","G"), sep = "([..///_])", extra = "merge") %>%
  separate(G, c("A1","B1","C1","D1","E1","F1","G1"), sep = "([._])", extra = "merge") %>%
  dplyr::select(F:A1, AREA:vs) %>%
  rename(climate_yr = F, climate_mon =A1)

df1
  
```




## Combine Temp Precip and snow

```{r}
df_climate = merge(df_temp_pr, snow_sel, by = c("ID_obj", "area_ha", "area_m", "fire_yr"))

```

```{r}
df_climate
```

```{r}
df_climate %>% summarise_all(~ sum(is.na(.)))
```

```{r}
na_data <- df_climate %>% filter_all(any_vars(is.na(.))) 
na_data
```

# Clean data
- Remove NA
- Scale temperature data
```{r}
df1
```

## Scale varaibles
***
### Data Details
[Terra Climate](https://developers.google.com/earth-engine/datasets/catalog/IDAHO_EPSCOR_TERRACLIMATE)

Name  |	Units	| Scale	| Description
------|-------|-------|------------
aet	  | mm	  |	0.1	  | Actual evapotranspiration,  
def	  | mm	  |	0.1	  | Climate water deficit, 
pdsi	|       |	0.01	| Palmer Drought Severity Index
pet	  | mm	  |	0.1	  | Reference evapotranspiration (ASCE Penman-Montieth)
pr	  | mm		|	      | Precipitation accumulation
ro	  | mm	  |       |	Runoff, 
soil	| mm	  | 0.1	  | Soil moisture, 
srad	| W/m^2	|	0.1	  | Downward surface shortwave radiation
swe	  | mm	  |		    | Snow water equivalent, 
tmmn	| 째C	  |	0.1	  | Minimum temperature
tmmx	| 째C	  |	0.1	  | Maximum temperature
vap	  | kPa	  |	0.001	| Vapor pressure
vpd   |	kPa	  |	0.01	| Vapor pressure deficit
vs	  | m/s	  |	0.01	| Wind-speed at 10m

***
```{r}
df_all = df1 %>% 
  mutate(aet= aet*0.1) %>%
  mutate(def = def*0.1) %>%
  mutate(pdsi= pdsi*0.01) %>%
  mutate(pet = pet*0.1) %>%
  mutate(soil = soil*0.1) %>%
  mutate(srad = srad*0.1) %>%
  mutate(tmmn = tmmn*0.1) %>%
  mutate(tmmx = tmmx*0.1) %>%
  mutate(vap = vap*0.001) %>%
  mutate(vpd = pet*0.01) %>%
  mutate(vs = vs*0.01) %>%
  mutate(fire_yr = as.factor(climate_yr))


df_all
```

```{r}
df2 = df1 %>% 
  na.omit() %>%
  mutate(tmmx= tmmx*0.1) %>%
  mutate(def = def*0.1) %>%
  mutate(fire_yr = as.factor(fire_yr))


df2
```


```{r}
df1_all = df_all %>% 
  pivot_wider(names_from = climate_mon, values_from = c(aet, def, pdsi, pet, pr, ro, soil, srad, swe, tmmn, tmmx, vap, vpd, vs))

df1_all
```

# Summarize data

```{r}
df_sum = df1_all %>% group_by(ECO_NAME) %>%
  select(def_jun, def_jul, def_aug, pdsi_jun, pdsi_jul, pdsi_aug, pr_jun, pr_jul, pr_aug) %>% # select variables to summarise
  summarise_each(funs(min = min, 
                      q25 = quantile(., 0.25), 
                      median = median, 
                      q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

head(df_sum)
```



# Visualize data

## Boxplots all varaibles

```{r}
plot1 = ggplot(df2, aes(x = fire_yr, y = tmp_mx, color=climate_mon)) +
  geom_boxplot() +
  theme_bw()

plot1
```

```{r}
plot2 = ggplot(df2, aes(x = fire_yr, y = pr, color=climate_mon)) +
  geom_boxplot() +
  theme_bw()

plot2
```

 

# Coorelations
```{r}
head(df2)

```

```{r}
qplot(data = df2, x=climate_yr, y=def, color = climate_mon)
```


```{r}
qplot(data = df2, x=climate_yr, y=tmmx, color = climate_mon)
```

```{r}
qplot(data = df2, x=climate_yr, y=pr, color = climate_mon)
```
```{r}
head(df2)
```

```{r}
df3 = df2 %>%
  dplyr::select(climate_yr:fire_yr, tmmx, pr)
df3
```


```{r}
df4 = df3 %>% 
  pivot_wider(names_from = climate_mon, values_from = c(aet, def, tmmx, pr))

df4
```






```{r}
df_climate1_corr = df4 %>%
  mutate(year = as.numeric(climate_yr)) %>%
  dplyr::select(area_ha, year, def_apr:pr_may)

```

```{r}
corr = round(cor(df_climate1_corr), 1)  
p_mat <- round(cor_pmat(df_climate1_corr), 3)
p_mat
```

```{r fig.height=6, fig.width=6}
cor_plot = ggcorrplot(corr)
cor_plot
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-27_CorrPlot_month_def-tmp-pr.jpeg", plot = cor_plot, width = 12, height = 11, units = c("in"), dpi=600 )
```


## All

```{r}
df1_all_corr = df1_all %>%
  mutate(year = as.numeric(climate_yr)) %>%
  dplyr::select(-climate_yr, -fire_yr)

```

```{r}
corr1 = round(cor(df1_all_corr), 1)  
p_mat1 <- round(cor_pmat(df1_all_corr), 3)
p_mat1
```

```{r}
cor_plot1 = ggcorrplot(corr1)
cor_plot1
```



```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-27_CorrPlot_month_all.jpeg", plot = cor_plot1,  width = 12, height = 11, units = c("in"), dpi=600 )
```

# Combine plots

```{r fig.height=11, fig.width=12}
vis1 = cowplot::plot_grid(plot1, plot4, plot2, plot5, plot3, plot6, plot7,  labels = "AUTO", align = "hv", label_size = 12, ncol= 2) + 
  theme(plot.margin = margin(0, 0, 0, 0)) 

vis1
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-01_Boxplot-Temp-PR-Snowoff.jpeg", plot = vis1, width = 12, height = 11, units = c("in"), dpi=600 )
```