---
title: "Ecozones"
author: "Anna Talucci"
date: "7/31/2020"
output: html_document
---
# Overview

# packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
library(raster)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "
```

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Data
```{r}
ecozone = st_read("../data/wwf_ecozone/wwf_terr_ecos_oRn.shp", "wwf_terr_ecos_oRn") 
```

```{r}

ne_bbox = st_read("../data/bbox/neSiberia_bbox.shp", "neSiberia_bbox") 

```


```{r}
bbox = readOGR("../data/bbox/neSiberia_bbox.shp", "neSiberia_bbox")
ez = readOGR("../data/wwf_ecozone/wwf_terr_ecos_oRn.shp", "wwf_terr_ecos_oRn")
```

# Filter (subset by ECO_NAME
```{r}
head(ecozone)
```

```{r}
biome = ecozone %>% filter(BIOME==11)
```

```{r}
unique(biome$ECO_NAME)
```

Cherskii-Kolyma mountain tundra 
Northeast Siberian coastal tundra 
Chukchi Peninsula tundra
Northeast Siberian taiga
Bering tundra
Taimyr-Central Siberian tundra
East Siberian taiga

Create Target with ECO_NAME associated with BIOME 11
```{r}
target = c("Cherskii-Kolyma mountain tundra", "Northeast Siberian coastal tundra","Chukchi Peninsula tundra", "Northeast Siberian taiga", "Bering tundra", "Taimyr-Central Siberian tundra", "East Siberian taiga")
```

```{r}
ne_subset = ecozone %>% filter(ECO_NAME %in% target) 
```

```{r}
summary(ne_subset)
```





## Plot Data

```{r}
plot(ne_subset$geometry)
```

```{r}
plot(ez)
```

```{r}
head(ez)
```
```{r}
unique(ez$REALM) 
```

```{r eval=FALSE, include=FALSE}
unique(ez$ECO_NAME) 
```
# Transform CRS

```{r}
ez_ee = spTransform(ez, CRS(ee_russia))
bbox_ee = spTransform(bbox, CRS(ee_russia))

```

# Subset to FLARE
```{r}
ez_subset <- ez_ee[bbox_ee, ]
plot(ez_subset)
```

# True clip (similar to ESRI)
```{r}
ne_subset_crop <-  st_crop(ne_subset, ne_bbox) #clip polygon 2 with polygon 1
head(ne_subset_crop)
```

```{r}
plot(ne_subset_clip$geometry)
```



# Transform CRS

```{r}
ez_subset_wgs = spTransform(ez_subset, CRS(wgs_proj))
```

# Clip to bbox

```{r}
ez_wgs_clip <- gIntersection(ez_subset_wgs, bbox, byid = TRUE, drop_lower_td = TRUE) #clip polygon 2 with polygon 1
plot(ez_wgs_clip, col = "lightblue")
```

```{r}
ez_wgs_clip <- gIntersection(ez_subset_wgs, bbox, byid = TRUE, drop_lower_td = TRUE) #clip polygon 2 with polygon 1
plot(ez_wgs_clip, col = "lightblue")
```

```{r}
ez_clip_wgs = spTransform(ez_clip, CRS(wgs_proj))
plot(ez_clip_wgs)
plot(bbox, add=TRUE)
```

```{r}
plot(ez_subset_wgs)
plot(bbox, add=TRUE)
```




## Sp to sf

```{r}
ez_subset_wgs_st = st_as_sf(ez_subset_wgs)

```


```{r}
ez_clip_wgs_st = st_as_sf(ez_clip_wgs)

```

# Write Shapefile

```{r}
st_write(ne_subset, "../outputs/ecozones/ne_siberia_ecozones.shp", driver="ESRI Shapefile") 
```

```{r}
st_write(ne_subset_clip, "../outputs/ecozones/ne_siberia_ecozones_crop.shp", driver="ESRI Shapefile") 
```

```{r}
st_write(ez_subset_wgs_st, "../outputs/ecozones/FLARE-Ecozones.shp", driver="ESRI Shapefile") 
```

```{r}
st_write(ez_clip_wgs_st, "../outputs/ecozones/FLARE-Ecozones-clip.shp", driver="ESRI Shapefile") 
```