---
title: "EcoZone Selection"
author: "Anna Talucci"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
This code uses the [WWF Ecozones shapefile](https://www.worldwildlife.org/publications/terrestrial-ecoregions-of-the-world). We subset the ecozones for NE Siberia to include the following:

1. Bering tundra
2. Chukchi peninsula tundra
3. Cherskii-Kolyma mountain tundra
4. East Siberia Tiaga
5. Northeast Siberia coastal Tundra
6. Northeast Siberia taiga
7. Taimyr-central Siberia tundra 
8. Trans-Baikal Bald Mountain Tundra

While we will need the attribute field for the final fire perimeters, they are not neccessary for the polygons we use in GEE.

Here we split the ecozones needed into individual polygon shapefile with a couple of exceptions. We will combine Cherskii-Kolyma mountain tundra and Northeast Siberia taiga into one polygon for GEE. We will also combine Bering tundra Chukchi peninsula tundra, which will then be split by east and west hemisphere. Treat East Siberia Tiaga and Trans-Baikal Bald Mountain Tundra as one spatial unit.

2021-03-19 -- add South Siberian forest steppe because of hole inside south easter portion of polygon

# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(spatialEco)
```

# Data
```{r}
ecozone = st_read("../data/wwf_ecozone/wwf_terr_ecos_oRn.shp", "wwf_terr_ecos_oRn") 
```

```{r}
head(ecozone)
```

```{r}
biome = ecozone %>% filter(BIOME==11)
```

```{r}
unique(biome$ECO_NAME)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Select ecozones for region of interest

## Create target of require ecozones 
1. Cherskii-Kolyma mountain tundra (CKMT)
2. Northeast Siberian coastal tundra (NSCT)
3. Chukchi Peninsula tundra (CPT)
4. Northeast Siberian taiga (NST)
5. Bering tundra (BT)
6. Taimyr-Central Siberian tundra (TCST)
7. East Siberian taiga (EST)
8. Trans-Baikal Bald Mountain tundra (TBBMT)
9. South Siberian forest steppe (SSFT)
```{r}
target = c("Cherskii-Kolyma mountain tundra", "Northeast Siberian coastal tundra","Chukchi Peninsula tundra", "Northeast Siberian taiga", "Bering tundra", "Taimyr-Central Siberian tundra", "East Siberian taiga", "Trans-Baikal Bald Mountain tundra", "South Siberian forest steppe")
```

## Apply filter

Filter for all
```{r}
ne_subset = ecozone %>% 
  filter(ECO_NAME %in% target) %>% 
  mutate(eco_code = ifelse(ECO_NAME %in% "Cherskii-Kolyma mountain tundra", "CKMT",
       ifelse(ECO_NAME %in% "Northeast Siberian coastal tundra", "NSCT",
          ifelse(ECO_NAME %in% "Chukchi Peninsula tundra", "CPT",
            ifelse(ECO_NAME %in% "Northeast Siberian taiga", "NST",
              ifelse(ECO_NAME %in% "Bering tundra", "BT",
                ifelse(ECO_NAME %in% "Taimyr-Central Siberian tundra", "TCST",
                  ifelse(ECO_NAME %in% "Trans-Baikal Bald Mountain tundra", "TBBMT",
                         ifelse(ECO_NAME %in% "East Siberian taiga", "EST",
            ifelse(ECO_NAME %in%  "South Siberian forest steppe", "SSFS", "NA"))))))))))
```


```{r}
ggplot(ne_subset) + geom_sf()
```

```{r}
ne_subset
```

```{r}
head(ne_subset)
```
```{r}
ne_subset$eco_code
```


```{r}
ne_subset %>%
  summarise_all(funs(sum(is.na(.))))
```

```{r}
ne_subset$eco_code
```

## ne_subset
```{r}
ne_subset_ee = st_transform(ne_subset, crs=ee_russia)
```

```{r}
  
ggplot(ne_subset_ee) + geom_sf()
```

## Save Shapefiles

```{r eval=FALSE, include=FALSE}
st_write(ne_subset_ee, "../outputs/ecozones/ne_siberia_ecozones9_ee.shp", driver="ESRI Shapefile") 
st_write(ne_subset, "../outputs/ecozones/ne_siberia_ecozones9.shp", driver="ESRI Shapefile") 
```


# Select individual Ecozones
## Filter individual ecozones
-- Cherskii-Kolyma mountain tundra (CKMT)
-- Northeast Siberian coastal tundra (NSCT)
-- Chukchi Peninsula tundra (CPT)
-- Northeast Siberian taiga (NST)
-- Bering tundra (BT)
-- Taimyr-Central Siberian tundra (TCST)
-- East Siberian taiga (EST)
-- Trans-Baikal Bald Mountain tundra (TBBMT)

Treat CKMT and NST as one spatial unit.
Treat CPT and BT as one spatail unit, but split by east/west hemisphere.
Treat EST and TBBMT as one spatial unit.


### Northeast Siberian coastal tundra (NSCT)
```{r}
nsct = ne_subset %>% 
  filter(eco_code %in% "NSCT")
```

```{r}
ggplot(nsct) + geom_sf()
```

### Taimyr-Central Siberian tundra (TCST)
```{r}
tcst = ne_subset %>% 
  filter(eco_code %in% "TCST")
```

```{r}
ggplot(tcst) + geom_sf()
```

### East Siberian taiga (EST) & Trans-Baikal Bald Mountain tundra (TBBMT)
```{r}
est_tbbmt = ne_subset %>% 
  filter(eco_code %in% c("EST", "TBBMT"))
```

```{r}
ggplot(est_tbbmt) + geom_sf()
```

### Cherskii-Kolyma mountain tundra (CKMT) & Northeast Siberian taiga (NST)

```{r}
ckmt_nst = ne_subset %>% 
  filter(eco_code %in% c("CKMT", "NST"))
```

```{r}
ggplot(ckmt_nst) + geom_sf()
```

### Chukchi Peninsula tundra (CPT) and Bering tundra (BT)
```{r}
cpt_bt_east = ne_subset %>% 
  filter(eco_code %in% c("CPT", "BT")) %>%
  filter(OBJECTID %in% c("4730", "4302"))
```

```{r}
cpt_bt_east
```
```{r}
ggplot(cpt_bt_east) + geom_sf()
```
```{r eval=FALSE, include=FALSE}
st_write(cpt_bt_east, "../outputs/ecozones/chukchi_east_west/cpt_bt_east.shp", driver="ESRI Shapefile")
```


```{r}
cpt_bt_west = ne_subset %>% 
  filter(eco_code %in% c("CPT", "BT")) %>%
  filter(OBJECTID %in% c("4890", "2692"))
```

```{r}
cpt_bt_west
```

```{r}
ggplot(cpt_bt_west) + geom_sf()
```

```{r eval=FALSE, include=FALSE}
st_write(cpt_bt_west, "../outputs/ecozones/chukchi_east_west/cpt_bt_west.shp", driver="ESRI Shapefile")
```



# Create individual polygons for GEE
Convert to equal area projection, buffer, dissolve, covert back to WSG84, save

-- nsct
-- tcst
-- est
-- ckmt_nst
-- cpt_bt_east
-- cpt_bt_west

## Covert to Equal Area projection
st_transform(x, crs = st_crs(x), ...)

```{r}
nsct_ee = st_transform(nsct, crs=ee_russia)
tcst_ee = st_transform(tcst, crs=ee_russia)
est_tbbmt_ee = st_transform(est_tbbmt, crs=ee_russia)
ckmt_nst_ee = st_transform(ckmt_nst, crs=ee_russia)
cpt_bt_east_ee = st_transform(cpt_bt_east, crs=ee_russia)
cpt_bt_west_ee = st_transform(cpt_bt_west, crs=ee_russia)

```


```{r}
ggplot(nsct_ee) + geom_sf()
```

## Buffer

```{r}
nsct_buf = st_buffer(nsct_ee, dist=3000, joinStyle="ROUND")
tcst_buf = st_buffer(tcst_ee, dist=3000, joinStyle="ROUND")
est_tbbmt_buf = st_buffer(est_tbbmt_ee, dist=3000, joinStyle="ROUND")
ckmt_nst_buf = st_buffer(ckmt_nst_ee, dist=3000, joinStyle="ROUND")
cpt_bt_east_buf = st_buffer(cpt_bt_east_ee, dist=3000, joinStyle="ROUND")
cpt_bt_west_buf = st_buffer(cpt_bt_west_ee, dist=3000, joinStyle="ROUND")
```


## Remove overlap between buffers
```{r}
nsct_dis = st_cast(st_union(nsct_buf),"POLYGON")
tcst_dis = st_cast(st_union(tcst_buf),"POLYGON")
est_tbbmt_dis = st_cast(st_union(est_tbbmt_buf),"POLYGON")
ckmt_nst_dis = st_cast(st_union(ckmt_nst_buf),"POLYGON")
cpt_bt_east_dis = st_cast(st_union(cpt_bt_east_buf),"POLYGON")
cpt_bt_west_dis = st_cast(st_union(cpt_bt_west_buf),"POLYGON")
```


## Save GEE Ecozone Polygons in Equal Area
```{r eval=FALSE, include=FALSE}
st_write(nsct_dis, "../outputs/ecozones/eco_ee/gee_eco_nsct_ee.shp", driver="ESRI Shapefile") 

st_write(tcst_dis, "../outputs/ecozones/eco_ee/gee_eco_tcst_ee.shp", driver="ESRI Shapefile")

st_write(est_tbbmt_dis, "../outputs/ecozones/eco_ee/gee_eco_est_tbbmt_ee.shp", driver="ESRI Shapefile")

st_write(ckmt_nst_dis, "../outputs/ecozones/eco_ee/gee_eco_ckmt_nst_ee.shp", driver="ESRI Shapefile")

st_write(cpt_bt_east_dis, "../outputs/ecozones/eco_ee/gee_eco_cpt_bt_east_ee.shp", driver="ESRI Shapefile")

st_write(cpt_bt_west_dis, "../outputs/ecozones/eco_ee/gee_eco_cpt_bt_west_ee.shp", driver="ESRI Shapefile")

```

#### Check buffer and dissolve effect
```{r}
ggplot(nsct_dis) + geom_sf()
```

```{r}
ggplot(tcst_dis) + geom_sf()
```

```{r}
ggplot(est_tbbmt_dis) + geom_sf()
```
```{r}
ggplot(ckmt_nst_dis) + geom_sf()
```

```{r}
ggplot(cpt_bt_west_dis) + geom_sf()
```
```{r}
ggplot(cpt_bt_east_dis) + geom_sf()
```

### Convert back to WSG 84 for GEE
```{r}
nsct_wgs = st_transform(nsct_dis, crs=wgs_proj)
tcst_wgs = st_transform(tcst_dis, crs=wgs_proj)
est_tbbmt_wgs = st_transform(est_tbbmt_dis, crs=wgs_proj)
ckmt_nst_wgs = st_transform(ckmt_nst_dis, crs=wgs_proj)
cpt_bt_east_wgs = st_transform(cpt_bt_east_dis, crs=wgs_proj)
cpt_bt_west_wgs = st_transform(cpt_bt_west_dis, crs=wgs_proj)
```

```{r}
ggplot(cpt_bt_west_wgs) + geom_sf()
```


# Bounding box details

-- Cherskii-Kolyma mountain tundra (CKMT)
-- Northeast Siberian taiga (NST)
```{r}
ckmt_nst_wgs
ggplot(ckmt_nst_wgs) +geom_sf()
```

-- Northeast Siberian coastal tundra (NSCT)
```{r}
nsct_wgs
ggplot(nsct_wgs) +geom_sf()
```

-- Chukchi Peninsula tundra (CPT)
-- Bering tundra (BT)

```{r}
cpt_bt_east_wgs
ggplot(cpt_bt_east_wgs) +geom_sf()
```

```{r}
cpt_bt_west_wgs
ggplot(cpt_bt_west_wgs) +geom_sf()
```

-- Taimyr-Central Siberian tundra (TCST)

```{r}
tcst_wgs
ggplot(tcst_wgs) +geom_sf()
```


-- East Siberian taiga (EST)
-- Trans-Baikal Bald Mountain tundra (TBBMT)

```{r}
est_tbbmt_wgs
ggplot(est_tbbmt_wgs) +geom_sf()
```


### Individual buffered ecozones for GEE
```{r eval=FALSE, include=FALSE}
st_write(nsct_wgs, "../outputs/ecozones/gee_ecozones_nsct.shp", driver="ESRI Shapefile") 

st_write(tcst_wgs, "../outputs/ecozones/gee_ecozones_tcst.shp", driver="ESRI Shapefile")

st_write(est_tbbmt_wgs, "../outputs/ecozones/gee_eco_est_tbbmt.shp", driver="ESRI Shapefile")

st_write(ckmt_nst_wgs, "../outputs/ecozones/gee_eco_ckmt_nst.shp", driver="ESRI Shapefile")

st_write(cpt_bt_east_wgs, "../outputs/ecozones/gee_eco_cpt_bt_east.shp", driver="ESRI Shapefile")

st_write(cpt_bt_west_wgs, "../outputs/ecozones/gee_eco_cpt_bt_west.shp", driver="ESRI Shapefile")

```
