---
title: "Fire starts and season"
author: "Anna Talucci"
date: "11/6/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Assembly fire perimeter shape files with attribute data from hotspot data and bioclimatic zones, and climate. Data  needs to include:
- Fire year
- Fire class size
- Fire start date (julian annual)
- Fire end date (julian annual)
- Bioclimatic zone (ecozone)
- Max temp
- Drought index
- Snow off date


# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(lubridate)
```

# Define graph Theme and color Palette 
```{r}
lb_theme = theme_bw() + theme(legend.position = "bottom") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```


##Fire perimeters
```{r}
poly_folder <- "../data/perimeter_summary/" 

    #--store shapefile names as a list
poly_shp_files <- list.files(poly_folder, pattern = "\\.shp$")
poly_shp_files

```


```{r}
# Reads in all shapefiles from Directory that include the string "_CDs".
poly_files <- list.files(poly_folder , pattern="\\.shp$", full.names=TRUE)
poly_files
```


```{r}
# Applies the function st_read from the sf package to each file saved as a character string to transform the file list to a list object.
perimeter_list <-lapply(poly_files, st_read)
```

```{r}
head(perimeter_list)
```

```{r}
perimeters_df = perimeter_list %>% dplyr::bind_rows()
```

```{r}
st_geometry(perimeters_df) <- NULL
```

```{r}
head(perimeters_df)
```


# Fire season

Annual average start day
average Season length
```{r}
fire_season1 = perimeters_df %>% group_by(fire_yr) %>%
  mutate(burn_days = (mx_jln_ - min_jln_dt)) %>%
  summarise(first_day = min(min_jln_dt), last_day = max(mx_jln_), avg_start_day = mean(min_jln_dt), avg_end_day = mean(mx_jln_), avg_burn_days = mean(burn_days)) %>%
  as.data.frame() %>%
  mutate(ssn_lngth = last_day - first_day)


```

```{r}

fire_season1
```
fire_area = as.data.frame(fire_area)
fire_area


['#a6611a','#dfc27d','#f5f5f5','#80cdc1','#018571']
```{r}
ggplot(fire_season1) +
  geom_line(aes(x=fire_yr, y=first_day), color = "#018571" , size=1) +
  geom_line(aes(x=fire_yr, y=last_day), color = "#a6611a" , size=1) +
  geom_line(aes(x=fire_yr, y=avg_start_day), color = "#80cdc1" , size=1) +
  geom_line(aes(x=fire_yr, y=avg_end_day), color = "#dfc27d" , size=1) +
  geom_hline(yintercept=152, color = "#fdae61", size=1, linetype = "longdash") +
  geom_hline(yintercept=243, color = "#fdae61", size=1, linetype = "longdash") +
  ylab("Julian Date") +
  theme_bw() +
  scale_x_continuous(name="Year", breaks=seq(2000, 2020,2)) +
  theme(legend.position="bottom")



```




```{r}
long_df = fire_season1 %>%
  dplyr::select(fire_yr, first_day, last_day, avg_start_day, avg_end_day) %>%
  pivot_longer(!fire_yr, names_to = "start_end", values_to = "date") 
  
```
```{r}
head(long_df)
```

geom_line(aes(x=fire_yr, y=first_day), color = "#018571" , size=1) +
  geom_line(aes(x=fire_yr, y=last_day), color = "#a6611a" , size=1) +
  geom_line(aes(x=fire_yr, y=avg_start_day), color = "#80cdc1" , size=1) +
  geom_line(aes(x=fire_yr, y=avg_end_day), color = "#dfc27d" , size=1) +

```{r fig.height=5, fig.width=6}
plot_season = ggplot(long_df, aes(x=fire_yr, y=date, color = start_end)) +
  geom_line(size=1) +
   scale_color_manual(values = c("#80cdc1", "#018571", "#a6611a",  "#dfc27d"),  breaks = c("first_day", "avg_start_day","avg_end_day", "last_day"), 
  labels = c("start", "mean start", "mean end", "end")) +
   
  geom_hline(yintercept=152, color = "#fdae61", size=1, linetype = "longdash") +
  geom_hline(yintercept=243, color = "#fdae61", size=1, linetype = "longdash") +

  ylab("Julian date") +
  theme_bw() +
  scale_x_continuous(name="Year", breaks=seq(2000, 2020,2)) +
  theme(legend.position="bottom") +
  guides(color=guide_legend(title="Fire season:")) +
  annotate(geom="text", x=2001.1, y=157, label="June 1", color="grey30") +
  annotate(geom="text", x=2001.6, y=249, label="August 31", color="grey30")


plot_season
``` 
  
```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-11-11_fire-season.png", plot = plot_season, width = 6, height = 5, units = c("in"), dpi=600 )
```