---
title: "GEE Vector Ecozone Attribute Creation"
author: "Anna Talucci"
date: "3/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Here we take the cleaned vectors of fire perimeters and add attributes, clip to ecozone extent, add ecozone attributes, designate as arctic or sub arctic, and add attributes from hotspot data (e.g., fire start).

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(tidyr)
library(spatialEco)
library(ggplot2)
library(lubridate)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "
```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## Fire perimeters

```{r}
fires = st_read("../data/GEE-clean-shapefiles-SingleEco/combine_ecozones_2001.shp", "combine_ecozones_2001") 
```

## Hotspots
```{r}
hotspots = st_read("../data/M6-march-october/M6_mar-oct_2001.shp", "M6_mar-oct_2001") 
```

## Ecozones Polygon
```{r}
ecozones = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee") 
```

## Arctic Polygon
Cropped ecozones to arctic circle for arctic designation. 

```{r}
eco_arctic = st_read("../data/bbox/ecozone_arctic_crop_ee.shp", "ecozone_arctic_crop_ee") 
```

# Convert to Equal Area

```{r}
fires_ee = st_transform(fires, ee_russia)
hotspots_ee = st_transform(hotspots, ee_russia)
ecozones_ee = st_transform(ecozones, ee_russia)
eco_arctic_ee = st_transform(eco_arctic, ee_russia)
```


# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr
- Removed fires less than 400 ha
- Ecozone
- Arctic/subarctic

## Area Burned Attributes
```{r}
fires_at = fires_ee %>%
  dplyr::mutate(ID_obj = row_number()) %>% 
  dplyr::mutate(burned_area_m = as.numeric(round(st_area(fires_ee),1))) %>% 
  dplyr::mutate(burned_area_ha = as.numeric(round(burned_area_m*0.0001, 1))) %>% 
  dplyr::mutate(fire_yr = 2001) 
```


```{r}
fires_at
```





```{r}
plot(st_geometry(ecozones_ee), col = sf.colors(12, categorical = TRUE), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at)), pch = 3, col = 'red', add = TRUE)
```

## Ecozone attributes

We use `st_join` to add the attributes of the ecozone for each fire. Fires are not restricted to within individual ecozone boundaries. In order to avoid a duplicate entry for a fire that spans two ecozones, we add the argument `largest=TRUE`, which assigns the ecozone that contrains the majority of the fire. 

```{r}
head(ecozones_ee)
```
### Rename columns for  ecozones
Note about  attributes
1. AREA - area for individual polygons
2. area_km^2 - total area for each ecoregion ( 1 km^ is 100 ha)
```{r}
ren_ecozones_ee = ecozones_ee %>% 
  rename(c("eco_objectID" = "OBJECTID", "eco_area" = "AREA" , "eco_realm" = "REALM", "eco_biome" = "BIOME")) %>%
  dplyr::mutate(eco_area_ha = as.numeric(round(area_km2*100, 1)))
```

### Join ecozone attributes with fire perimeters
```{r}
fires_at_eco = st_join(fires_at, ren_ecozones_ee, largest=TRUE) %>% dplyr::select(FID:eco_area, ECO_NAME:ECO_SYM, area_km2:geometry) %>% drop_na(eco_code)
```

```{r}
head(fires_at_eco)
```

```{r}
plot(st_geometry(ecozones_ee), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco)), pch = 3, col = 'red', add = TRUE)
```

## Arctic/Subarctic designation
```{r}
fires_at_eco_arc = st_join(fires_at_eco, eco_arctic_ee, largest=TRUE) 
```

```{r}
str(fires_at_eco_arc)
```

### Convert NA to subarctic
For location, arctic and subarctic, we need to redefine the NA values as subartic
```{r}
fires_at_eco_arc$location <- factor(fires_at_eco_arc$location, exclude = NULL, 
               levels = c("arctic", NA), 
               labels = c("arctic", "subarctic"))
fires_at_eco_arc
```

```{r}
plot(st_geometry(ecozones_ee), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc)), pch = 3, col = 'red', add = TRUE)
```

### Save as test version to check
```{r eval=FALSE, include=FALSE}
st_write(fires_at_eco_arc, "../outputs/test/test_fires_at_eco_arc.shp", driver="ESRI Shapefile") 

```

## Hotspot attributes
```{r}
str(hotspots_ee)
```

```{r}
hotspots_ee %>% mutate(julian_date = yday(ACQ_DATE)) %>% 
  separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) 
```


### Function to summarize hotspot attributes
```{r}
sum_pt_poly = function(x){
  x %>% mutate(julian_date = yday(ACQ_DATE)) %>%
  separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) %>% group_by(ID_obj) %>% 
  summarize(min_julian_date = min(julian_date),
            max_julian_date = max(julian_date),
            mean_julian_date = mean(julian_date),
            median_julian_date = median(julian_date),
            min_confidence = min(CONFIDENCE), 
            max_confidence = max(CONFIDENCE), 
            mean_confidence = mean(CONFIDENCE), 
            median_confidence = median(CONFIDENCE),
            min_acq_date = min(ACQ_DATE), 
            max_acq_date = max(ACQ_DATE)) -> x
  return(x)
}
```


```{r}
fires_at_eco_arc_hs = st_intersection(hotspots_ee, fires_at_eco_arc) %>% sum_pt_poly()

```

```{r}
head(fires_at_eco_arc_hs)
```
```{r}
plot(st_geometry(ecozones_ee), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc_hs)), pch = 3, col = 'red', add = TRUE)
```
### Drop geometry from hotspot attributes

```{r}
st_geometry(fires_at_eco_arc_hs) <- NULL
```

## Merge  attributes
Merge attributes into single shapefile
```{r}
fires_at_eco_arc_hs_merge = merge(fires_at_eco_arc, fires_at_eco_arc_hs, by="ID_obj")
```

```{r}
head(fires_at_eco_arc_hs_merge)
```


```{r}
plot(st_geometry(ecozones_ee), border = 'grey', 
     axes = TRUE)
plot(st_geometry(st_centroid(fires_at_eco_arc_hs_merge)), pch = 3, col = 'red', add = TRUE)
```


## Add unique fire ID

```{r}
head(fires_at_eco_arc_hs_merge)
```
Fire ID components
1. RU
2. YEAR
3. Ecozone code
4. Start date

An add fire length in days

```{r}
fires_at_eco_arc_hs_merge_burn = fires_at_eco_arc_hs_merge %>%
  separate(min_acq_date, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) %>%
  mutate(burn_days = (max_julian_date - min_julian_date)) %>%
  mutate(Fire_ID = paste("RU_", fire_yr,"_", eco_code, "_", acq_year, acq_month, acq_day, sep = "")) 

```




# Remove geometry and write attributes to CSV
```{r eval=FALSE, include=FALSE}
fires_at_eco_arc_hs_merge %>% 
  st_set_geometry(NULL) %>% 
        write.csv(., '../outputs/test/test_attributes.csv',  row.names = FALSE)
  
```

# Write to shapefile
## Save  test version to inspect 
```{r eval=FALSE, include=FALSE}
st_write(fires_at_eco_arc_hs_merge_burn, "../outputs/GEE-Attribute-Shapefiles/ru-fires-2001.shp", driver="ESRI Shapefile") 

```