---
title: "Fire Activity Data Organization"
author: "Anna Talucci"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Assembly fire perimeter shape files with attribute data from hotspot data and bioclimatic zones, and climate. Data  needs to include:
- FIre year
- Fire class size
- Fire start date
- Fire end date
- Bioclimatic zone (ecozone)
- Max temp
- Drought index
- Snow off date

# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
```

# Read in Data  (Automated)
Read in multiple data files
f01 = st_read("../data/clean-shapefile/flare_30m/fires2001.shp", "fires2001") 
```{r eval=FALSE, include=FALSE}
fire_path <- "../data/clean-shapefile/flare_30m"   # path to the data
fire_files <- list.files(fire_path, pattern = "\\.shp$") # get file names
month_files
```

 replace with your folder name:
dir <- "c:/files/shpfiles"
ff <- list.files(dir, pattern="\\.shp$", full.names=TRUE)



```{r eval=FALSE, include=FALSE}
month_data <- month_files %>%
  # read in all the files, appending the path before the filename
  map(~ read_csv(file.path(month_path, .), .id = "file_name")) %>% 
  reduce(rbind)
month_data
```
map_df(~read_csv(.x, col_types = cols(), col_names = FALSE), .id = "file_name")


```{r eval=FALSE, include=FALSE}
list_of_files <- list.files(path = "../data/climate_monthly",
                            full.names = TRUE)
list_of_files
df <- list_of_files %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name")     
df
```
 separate(file_name, c("A","B","C"), sep = "([.?:])")
```{r eval=FALSE, include=FALSE}
df1 = df %>% 
  separate(file_name, c("A","B","C","D","E","F","G"), sep = "([..///_])", extra = "merge") %>%
  separate(G, c("A1","B1","C1","D1","E1","F1","G1"), sep = "([._])", extra = "merge") %>%
  dplyr::select(A1:B1, ID_obj:vs) %>%
  rename(climate_yr = A1, climate_mon = B1)

df1
  
```

# Read in one fire year are test extracting attributes
```{r}
perimeter = st_read("../data/clean-shapefile/flare_30m/fires2001.shp", "fires2001") 
```

```{r}
hotspot = st_read("../data/hotspot_data/DL_FIRE_M6_2001/fire_archive_2001.shp", "fire_archive_2001") 
```

```{r}
head(hotspot)
```

```{r}
head(perimeter)  # polygons
head(hotspot) # points
plot(perimeter)
plot(hotspot, add=TRUE)
```

```{r}
test = st_intersection(hotspot, perimeter)
```

```{r}
summary(test)
```



```{r}
test_sum = test %>% separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-") %>% group_by(ID_obj) %>% 
  summarize(min_acq_month = min(acq_month),
            min_acq_day = min(acq_day), max_acq_month = max(acq_month),
            max_acq_day = max(acq_day), mean_confidence = mean(CONFIDENCE), min_confidence = min(CONFIDENCE), max_confidence = max(CONFIDENCE)) 
```

```{r}
st_geometry(test_sum) <- NULL
```

```{r}
head(test_sum)
```
```{r}
merge(perimeter, test_sum, by="ID_obj")
```


*************************************
point.in.poly(point, poly)
```{r}
pts.poly <- point.in.poly(hotspot, perimeter)
summary(pts.poly)
```

```{r}
pts.poly
```

```{r}
pts.poly2 = na.omit(pts.poly)
head(pts.poly2)
summary(pts.poly2)
```

```{r}
ecozone
```


```{r}
climate
```


# Spatial Analysis Test
https://gis.stackexchange.com/questions/137621/join-spatial-point-data-to-polygons-in-r
```{r}
require(spatialEco)
require(sp)
data(meuse)
coordinates(meuse) = ~x+y
sr1=Polygons(list(Polygon(cbind(c(180114, 180553, 181127, 181477, 181294, 181007, 180409,
  180162, 180114), c(332349, 332057, 332342, 333250, 333558, 333676,
  332618, 332413, 332349)))),'1')
sr2=Polygons(list(Polygon(cbind(c(180042, 180545, 180553, 180314, 179955, 179142, 179437,
  179524, 179979, 180042), c(332373, 332026, 331426, 330889, 330683,
  331133, 331623, 332152, 332357, 332373)))),'2')
sr3=Polygons(list(Polygon(cbind(c(179110, 179907, 180433, 180712, 180752, 180329, 179875,
  179668, 179572, 179269, 178879, 178600, 178544, 179046, 179110),
  c(331086, 330620, 330494, 330265, 330075, 330233, 330336, 330004,
  329783, 329665, 329720, 329933, 330478, 331062, 331086)))),'3')
sr4=Polygons(list(Polygon(cbind(c(180304, 180403,179632,179420,180304),
  c(332791, 333204, 333635, 333058, 332791)))),'4')
sr=SpatialPolygons(list(sr1,sr2,sr3,sr4))
srdf=SpatialPolygonsDataFrame(sr, data.frame(row.names=c('1','2','3','4'), PIDS=1:4, y=runif(4)))
```

```{r}
head(srdf@data)  # polygons
head(meuse@data) # points
plot(srdf)
points(meuse, pch=20)
```

```{r}
 pts.poly <- point.in.poly(meuse, srdf)
    head(pts.poly@data)
```

```{r}
srdf@data$poly.ids <- 1:nrow(srdf) 
```

```{r}
# Number of points in each polygon
tapply(pts.poly@data$lead, pts.poly@data$PIDS, FUN=length)

# Mean lead in each polygon
tapply(pts.poly@data$lead, pts.poly@data$PIDS, FUN=mean)
```



