---
title: "Fire Activity Data Organization"
author: "Anna Talucci"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Assembly fire perimeter shape files with attribute data from hotspot data and bioclimatic zones, and climate. Data  needs to include:
- Fire year
- Fire class size
- Fire start date (julian annual)
- Fire end date (julian annual)
- Bioclimatic zone (ecozone)
- Max temp
- Drought index
- Snow off date




# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(lubridate)
```
https://stackoverflow.com/questions/47784656/batch-load-shapefiles-from-directory-into-r

https://stackoverflow.com/questions/62419562/read-in-a-list-of-shapefiles-and-row-bind-them-in-r-preferably-using-tidy-synta

# Data
## Individual files

```{r}
fire2001 = st_read("../data/clean-shapefile/flare_30m/fires2001.shp", "fires2001")
fire2002 = st_read("../data/clean-shapefile/flare_30m/fires2002.shp", "fires2002")
```

```{r}
hotspot2001 = st_read("../data/hotspot_data/DL_FIRE_M6_2001/fire_archive_2001.shp", "fire_archive_2001") 
hotspot2002 = st_read("../data/hotspot_data/DL_FIRE_M6_2002/fire_archive_2002.shp", "fire_archive_2002") 
```

##Fire perimeters
```{r}
poly_folder <- "../data/clean-shapefile/flare_30m/" 

    #--store shapefile names as a list
poly_shp_files <- list.files(poly_folder, pattern = "\\.shp$")
poly_shp_files

```


```{r}
# Reads in all shapefiles from Directory that include the string "_CDs".
poly_files <- list.files(poly_folder , pattern="\\.shp$", full.names=TRUE)
poly_files
```


```{r}
# Applies the function st_read from the sf package to each file saved as a character string to transform the file list to a list object.
perimeter_list <-lapply(poly_files, st_read)
```

```{r}

for (i in seq(perimeter_list))
      assign(paste("fire_", i+2000, sep = ""), perimeter_list[[i]])
```

```{r}
head(fire_2019)
```





## Hotspots
```{r}
point_folder <- "../data/hotspot_data/hotspots_shp" 

    #--store shapefile names as a list
    point_shp_files <- list.files(point_folder, pattern = "\\.shp$", full.names = TRUE)

    #--inspect list
    #print(shp_files)
```

```{r}
point_folder <- "../data/hotspot_data/hotspots_shp/" 

    #--store shapefile names as a list
point_shp_files <- list.files(point_folder, pattern = "\\.shp$")
point_shp_files

```


```{r}
# Reads in all shapefiles from Directory that include the string "_CDs".
point_files <- list.files(point_folder , pattern="\\.shp$", full.names=TRUE)
point_files
```


```{r}
# Applies the function st_read from the sf package to each file saved as a character string to transform the file list to a list object.
hotspot_list <-lapply(point_files, st_read)
```

```{r}

for (i in seq(hotspot_list))
      assign(paste("hotspot_", i+2000, sep = ""), hotspot_list[[i]])
```

```{r}
head(hotspot_2019)
```


# Part 1: Overlay
Overlay hotspot and  fire perimeter data by year in order to add attributes from hotspots to fire perimeters  that they interect. This will add attributes for:
- Fire start
- Fire end
- Accuracy


## Functions For overlay

Function for overlay and itentifying in
```{r}
f_intersect = function(point,polygon) {
  df_int = st_intersection(point, polygon)
  
  return(df_int)
}
```

This function summarizes the point data (i.e., hotspot data) per polygon (i.e., fire perimeters). We convert dates to annual julian day (0-365[6]) to have an stimated fire start and fire end date. We group by the polygon id (ID_obj) to calculate summaries for the point data within the polygon data. 

```{r}
sum_pt_poly = function(x){
  x %>% mutate(julian_date = yday(ACQ_DATE)) %>%
  separate(ACQ_DATE, c("acq_year","acq_month", "acq_day"), sep = "-", remove=FALSE) %>% group_by(ID_obj) %>% 
  summarize(min_julian_date = min(julian_date),
            max_julian_date = max(julian_date),
            mean_julian_date = mean(julian_date),
            median_julian_date = median(julian_date),
            min_acq_month = min(acq_month),
            min_acq_day = min(acq_day), 
            max_acq_month = max(acq_month),
            max_acq_day = max(acq_day), 
            min_confidence = min(CONFIDENCE), 
            max_confidence = max(CONFIDENCE), 
            mean_confidence = mean(CONFIDENCE), 
            median_confidence = median(CONFIDENCE)) -> x
  return(x)
}
```


## Apply functions

```{r}
sum_2001 = st_intersection(hotspot_2001, fire_2001) %>% sum_pt_poly()
sum_2002 = st_intersection(hotspot_2002, fire_2002) %>% sum_pt_poly()
sum_2003 = st_intersection(hotspot_2003, fire_2003) %>% sum_pt_poly()
sum_2004 = st_intersection(hotspot_2004, fire_2004) %>% sum_pt_poly()
sum_2005 = st_intersection(hotspot_2005, fire_2005) %>% sum_pt_poly()
```

```{r}
sum_2006 = st_intersection(hotspot_2006, fire_2006) %>% sum_pt_poly()
sum_2007 = st_intersection(hotspot_2007, fire_2007) %>% sum_pt_poly()
sum_2008 = st_intersection(hotspot_2008, fire_2008) %>% sum_pt_poly()
sum_2009 = st_intersection(hotspot_2009, fire_2009) %>% sum_pt_poly()
sum_2010 = st_intersection(hotspot_2010, fire_2010) %>% sum_pt_poly()
```

```{r}
sum_2011 = st_intersection(hotspot_2011, fire_2011) %>% sum_pt_poly()
sum_2012 = st_intersection(hotspot_2012, fire_2012) %>% sum_pt_poly()
sum_2013 = st_intersection(hotspot_2013, fire_2013) %>% sum_pt_poly()
sum_2014 = st_intersection(hotspot_2014, fire_2014) %>% sum_pt_poly()
sum_2015 = st_intersection(hotspot_2015, fire_2015) %>% sum_pt_poly()
```

```{r}
sum_2016 = st_intersection(hotspot_2016, fire_2016) %>% sum_pt_poly()
sum_2017 = st_intersection(hotspot_2017, fire_2017) %>% sum_pt_poly()
sum_2018 = st_intersection(hotspot_2018, fire_2018) %>% sum_pt_poly()
sum_2019 = st_intersection(hotspot_2019, fire_2019) %>% sum_pt_poly()
sum_2020 = st_intersection(hotspot_2020, fire_2020) %>% sum_pt_poly()
```

## remove geometry
Remove Geometry from dataframe in order to merge dataframe with polygon perimeters
```{r}
st_geometry(sum_2001) <- NULL
st_geometry(sum_2002) <- NULL
st_geometry(sum_2003) <- NULL
st_geometry(sum_2004) <- NULL
st_geometry(sum_2005) <- NULL
```

```{r}
st_geometry(sum_2006) <- NULL
st_geometry(sum_2007) <- NULL
st_geometry(sum_2008) <- NULL
st_geometry(sum_2009) <- NULL
st_geometry(sum_2010) <- NULL
```

```{r}
st_geometry(sum_2011) <- NULL
st_geometry(sum_2012) <- NULL
st_geometry(sum_2013) <- NULL
st_geometry(sum_2014) <- NULL
st_geometry(sum_2015) <- NULL
```

```{r}
st_geometry(sum_2016) <- NULL
st_geometry(sum_2017) <- NULL
st_geometry(sum_2018) <- NULL
st_geometry(sum_2019) <- NULL
st_geometry(sum_2020) <- NULL
```

```{r}
head(sum_2001)
```
 Merge new dataframe with fire perimeter dataframe
```{r}
perimeter2001 = merge(fire_2001, sum_2001, by="ID_obj")
perimeter2002 = merge(fire_2002, sum_2002, by="ID_obj")
perimeter2003 = merge(fire_2003, sum_2003, by="ID_obj")
perimeter2004 = merge(fire_2004, sum_2004, by="ID_obj")
perimeter2005 = merge(fire_2005, sum_2005, by="ID_obj")
```

```{r}
perimeter2006 = merge(fire_2006, sum_2006, by="ID_obj")
perimeter2007 = merge(fire_2007, sum_2007, by="ID_obj")
perimeter2008 = merge(fire_2008, sum_2008, by="ID_obj")
perimeter2009 = merge(fire_2009, sum_2009, by="ID_obj")
perimeter2010 = merge(fire_2010, sum_2010, by="ID_obj")
```

```{r}
perimeter2011 = merge(fire_2011, sum_2011, by="ID_obj")
perimeter2012 = merge(fire_2012, sum_2012, by="ID_obj")
perimeter2013 = merge(fire_2013, sum_2013, by="ID_obj")
perimeter2014 = merge(fire_2014, sum_2014, by="ID_obj")
perimeter2015 = merge(fire_2015, sum_2015, by="ID_obj")
```

```{r}
perimeter2016 = merge(fire_2016, sum_2016, by="ID_obj")
perimeter2017 = merge(fire_2017, sum_2017, by="ID_obj")
perimeter2018 = merge(fire_2018, sum_2018, by="ID_obj")
perimeter2019 = merge(fire_2019, sum_2019, by="ID_obj")

perimeter2020 = merge(fire_2020, sum_2020, by="ID_obj")

```

# Write shapefiles
```{r eval=FALSE, include=FALSE}
st_write(perimeter2001, "../outputs/perimeter_summary/perimeters2001.shp", driver="ESRI Shapefile") 
st_write(perimeter2002, "../outputs/perimeter_summary/perimeters2002.shp", driver="ESRI Shapefile") 
st_write(perimeter2003, "../outputs/perimeter_summary/perimeters2003.shp", driver="ESRI Shapefile") 
st_write(perimeter2004, "../outputs/perimeter_summary/perimeters2004.shp", driver="ESRI Shapefile") 
st_write(perimeter2005, "../outputs/perimeter_summary/perimeters2005.shp", driver="ESRI Shapefile") 
```

```{r eval=FALSE, include=FALSE}
st_write(perimeter2006, "../outputs/perimeter_summary/perimeters2006.shp", driver="ESRI Shapefile") 
st_write(perimeter2007, "../outputs/perimeter_summary/perimeters2007.shp", driver="ESRI Shapefile") 
st_write(perimeter2008, "../outputs/perimeter_summary/perimeters2008.shp", driver="ESRI Shapefile") 
st_write(perimeter2009, "../outputs/perimeter_summary/perimeters2009.shp", driver="ESRI Shapefile") 
st_write(perimeter2010, "../outputs/perimeter_summary/perimeters2010.shp", driver="ESRI Shapefile") 
```

```{r eval=FALSE, include=FALSE}
st_write(perimeter2011, "../outputs/perimeter_summary/perimeters2011.shp", driver="ESRI Shapefile") 
st_write(perimeter2012, "../outputs/perimeter_summary/perimeters2012.shp", driver="ESRI Shapefile") 
st_write(perimeter2013, "../outputs/perimeter_summary/perimeters2013.shp", driver="ESRI Shapefile") 
st_write(perimeter2014, "../outputs/perimeter_summary/perimeters2014.shp", driver="ESRI Shapefile") 
st_write(perimeter2015, "../outputs/perimeter_summary/perimeters2015.shp", driver="ESRI Shapefile") 
```

```{r eval=FALSE, include=FALSE}
st_write(perimeter2016, "../outputs/perimeter_summary/perimeters2016.shp", driver="ESRI Shapefile") 
st_write(perimeter2017, "../outputs/perimeter_summary/perimeters2017.shp", driver="ESRI Shapefile") 
st_write(perimeter2018, "../outputs/perimeter_summary/perimeters2018.shp", driver="ESRI Shapefile") 
st_write(perimeter2019, "../outputs/perimeter_summary/perimeters2019.shp", driver="ESRI Shapefile") 
st_write(perimeter2020, "../outputs/perimeter_summary/perimeters2020.shp", driver="ESRI Shapefile") 
```