---
title: "Trouble shoot hotspot 2003 hole issue"
author: "Anna Talucci"
date: "7/31/2020"
output: html_document
---

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Creat Bounding Box for FLARE
coords = matrix(c(118.94, 72.26,
               171.0, 72.26,
               171.0, 60.0, 
               118.94, 60.0), 
             ncol = 2, byrow = TRUE)
```{r}


coords = matrix(c(118.0, 74.26,
               190.25, 74.26,
               190.25, 60.0, 
               118.0, 60.0), 
             ncol = 2, byrow = TRUE)


P1 = Polygon(coords)
Ps1 = SpatialPolygons(list(Polygons(list(P1), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(Ps1)
```

```{r}
Ps1_sp_ee = spTransform(Ps1, CRS( ee_russia))
```

# Read in hotspot data

```{r}

hs2003 = readOGR("../data/hotspot_data/DL_FIRE_M6_2003/fire_archive_2003.shp", "fire_archive_2003") 

```
```{r}
plot(hs2003)
```

## project to equal area russia
```{r}
hs2003_ee = spTransform(hs2003, CRS(ee_russia))
```
## Reduce hotspot data to FLARE  BBox



```{r}
hs2003_ee_sub = hs2003_ee[Ps1_sp_ee, ]
```
# Buffer by 3k

```{r}
hs2003_ee_3k = gBuffer(hs2003_ee_sub, width = 3000, capStyle="ROUND", joinStyle="ROUND")
```


```{r}
plot(hs2003_ee_3k)
```




## SP to sf
```{r}
hs2003_ee_3k_sf = st_as_sf(hs2003_ee_3k)
```

```{r}
hs2003_ee_3k_sf_wgs = st_transform(hs2003_ee_3k_sf, wgs_proj)
```

```{r}

hs2003_wgs_3k_nh = st_multipolygon(lapply(hs2003_ee_3k_sf_wgs, function(x) x[1]))
```

```{r}
st_write(hs2003_ee_3k_sf, "../outputs/hotspot-poly/Hole-Issue-hs2003_ee_3k_2001.shp", driver="ESRI Shapefile") 
```

```{r}

hs2003_ee_3k_sf_nh = st_multipolygon(lapply(hs2003_ee_3k_sf, function(x) x[1]))
```



***
## project to equal area russia
```{r}
hs2003_ee = spTransform(hs2003, CRS(ee_russia))
```
## Reduce hotspot data to FLARE  BBox



```{r}
hs2003_ee_sub = hs2003_ee[Ps1_sp_ee, ]
```
# Buffer by 3k

```{r}
hs2003_ee_3k = gBuffer(hs2003_ee_sub, width = 3000, capStyle="ROUND", joinStyle="ROUND")
```

```{r}
plot(hs2003_ee_3k)
```

## Remove holes in polygons

```{r}

hs2003_ee_3k_nh = remove.holes(hs2003_ee_3k)
```

## reproject to WGS for GEE

```{r}

hs2003_ee_3k_wgs = spTransform(hs2003_ee_3k_nh, CRS( wgs_proj))

```

```{r}
plot(hs2003_ee_3k_wgs)
```


## Sp to sf


```{r}

hs2003_3k_wgs = st_as_sf(hs2003_ee_3k_wgs)

```

## Trouble shooting
```{r}
require(devtools)
install_github("eblondel/cleangeo")
require(cleangeo)
```
```{r}
#trying to address issue with hs2003_ee_3k_wgs
report <- clgeo_CollectionReport(hs2003_ee_3k_wgs)
summary <- clgeo_SummaryReport(report)
issues <- report[report$valid == FALSE,]
issues
#get suspicious features (indexes)
nv <- clgeo_SuspiciousFeatures(report)
mysp <- hs2003_ee_3k_wgs[nv[-14],]

#try to clean data
mysp.clean <- clgeo_Clean(mysp)

#check if they are still errors
report.clean <- clgeo_CollectionReport(mysp.clean)
summary.clean <- clgeo_SummaryReport(report.clean)
report.clean
```
```{r}
mysp <- hs2003_ee_3k_wgs[-325,]
mysp.clean <- clgeo_Clean(mysp)

#check if they are still errors
report.clean <- clgeo_CollectionReport(mysp.clean)
summary.clean <- clgeo_SummaryReport(report.clean)
```
```{r}
pl2 <- st_multipolygon(lapply(hs2003_ee_3k_wgs, function(x) x[1]))
```
